### 2017-05-19 sigplan conf format paper/sections/Overview.tex
change format to Springer LNCS

\subsection{Solution in our language}
\begin{lstlisting}

\end{lstlisting}

\subsection{Method refinement}

>>>>

\subsection{Solution in our language}
\begin{lstlisting}
interface Deck {
   void draw() { // draws a card from the Deck }
}
interface Drawable {
   void draw() { // draws something on the screen }
}
interface DrawableDeck extends Deck, Drawable {
  //both draw() methods are kept automaticlaly in our language
} 
new DrawableDeck().Deck::draw()
\end{lstlisting}

\subsection{Method refinement}
\begin{lstlisting}
interface DrawableDeck2 extends DrawableDeck {
   void draw() override Deck {
      // new implementation of draw a card from deck
   }
   void draw() override Drawable {
      // new implementation of drawing something
   } 
} 
new DrawableDeck2().Deck::draw()
\end{lstlisting}
